---
title: "Week 1"
author: "Kevin Chu"
date: "2017/8/14"
output:
  rmarkdown::html_document:
    toc: true
  vignette: >  
    %\VignetteIndexEntry{Calculating statistics}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing Bioconductor

Install the latest release of R, then get the latest version of Bioconductor by starting R and entering the commands.

```{r cars, eval=FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite()
```

## Useful Online Resources

You can find a lot useful online resources in:

* The [Bioconductor support site](https://support.bioconductor.org)
* The [Stackoverflow](https://stackoverflow.com/search?q=bioconductor)
* The [rdocumentation](https://www.rdocumentation.org)
* The [rseek](www.rseek.org)

## GRanges - Overview
A GRanges is a data structure for storing genomic intervals.
## IRanges - Basic Usage


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
